The abundance of Bullet Groups in $\Lambda$CDM

### 2014-03-10 paper/ms.tex
abstract and results

We estimate the expected distribution of displacements between the two
dominant dark matter peaks in halos within a mass range corresponding
to galaxy groups. We find that 5\% to 25\% of the dark matter systems
with circular velocities in the range $300\kms$ to $700\kms$ show
multimodal morphologies with displacements between the dark matter
clumps equal or larger to $\sim 400$\hkpc, which corresponds to the
observational constraint the object SL2S J08544-0121 located at
$z=0.35$. 
\end{abstract}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{Figures_eps/figure_2.eps}
\end{center}
\caption{
  Integrated probability distribution for the displacement
  between the host halo and its dominand sub-halo. The left panel
  shows the results in terms of the physical displacements and the
  right panel the same displacement normalized by the virial radius of
  the host halo. The continuous line corrresponds to the halos in the
  group sample $V_{\rm circ,host}>700\kms$ and the dashed lines to the
  sample $V_{\rm circ,host}<700\kms$.
  The vertical stripe corresponds to the estimate of the separation
  between the two dark matter clumps in the results reported by
  \citet{Gastaldello} for the group SL2S J08544-0121. The right panel
  shows the same results normalized by the virial radius of the host
  halo.} 
\label{fig:displacement}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{Figures_eps/figure_5.eps} 
\end{center}
\caption{2D histogram in the plane $V_{\rm c,sub}/V_{\rm
    c,host}$-$d_{2D}$. The left panel corresponds to groups and the
  right panel to clusters. The circle with error bars corresponds to
  \bullg data reported from \citet{2013A&A...552A..80M} and
  \citet{Gastaldello}. The data used to construct the histograms
  integrates the objects at all redshifts. }
\label{fig:mass_displacement}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{Figures_eps/figure_3.eps}
\end{center}
\caption{Integrated probability distribution for the relative velocity of the
sub-halo with respect to its host. The left panel shows the results
in physical units while the right panel show the same values
normalized by the circular velocity of the host halo. The line coding
follows the same structure as Figure \ref{fig:displacement}}
\label{fig:velocities}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{Figures_eps/figure_4.eps}
\end{center}
\caption{x}
\label{fig:geometry}
\end{figure*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Figures_eps/figure_7.eps}
\end{center}
\caption{Integrated probability distribution for the estimated
  baryonic displacements in the group and cluster samples at all redshifts.}
\label{fig:baryonic_displacements}
\end{figure}

@@

The results for the integrated distributions for $>d_{2D}^{\rm bar}$
are shown in Figure \ref{fig:baryonic_displacements}.[..]

In order to facilitate the reproducibility and reuse of our results we
have made available all the data and the source code available in a public
repository. [...]

>>>>

We estimate the expected distribution of displacements between the two
dominant dark matter peaks in two groups of halos corresponding to
galaxy groups and clusters. We find that 50\% to 60\% of the dark
matter  with circular velocities in the range $300\kms$ to $700\kms$
(groups) show multimodal morphologies with displacements between the
dark matter clumps equal or larger than $133\pm21$\hkpc, which
corresponds to the observational constraint the object SL2S
J08544-0121 located at $z=0.35$ which hass a velocity dispersion of
$644^{+69}_{-102}\kms$. For dark matter halos with circular velocities
larger than $700\kms$ (clusters) this fraction rises to $80\%$ to
$85\%$. Using the same simulation we estimate the dark
matter-to-baryon spatial separation and find that that $0.1\%$ to
$1.0\%$ of the low mass systems should present separations equal or
larger than $87\pm 14$\hkpc corresponding to the same observational
benchmark; for halos with circular velocities larger than $700\kms$
this fraction is in the range of $4\%$ to $10\%$, consistent with
previous studies of dark mattter to baryon separations in
clusters. These results present a weak dependence with redshift. 
\end{abstract}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{figure_1.eps}
\end{center}
\caption{
  Integrated probability distribution for the displacement
  between the host halo and its largest sub-halo. The left panel
  shows the results in terms of the physical displacements while
  the right panel shows the displacements normalized by the virial radius of
  the host halo. The continuous line corrresponds to the halos in the
  group sample $V_{\rm circ,host}>700\kms$ and the dashed lines to the
  sample $V_{\rm circ,host}<700\kms$.
  The vertical lines corresponds to mean estimate separation 
  between the two dark matter clumps in the results reported by
  \citet{Gastaldello} for the group SL2S J08544-0121. Between $50\%$
  to $60\%$ of the groups show a displacement equal or larger than
  this observational benchmark.}
\label{fig:displacement}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{figure_2.eps} 
\end{center}
\caption{2D histogram in the plane $V_{\rm c,sub}/V_{\rm
    c,host}$-$d_{2D}$. The left panel corresponds to groups and the
  right panel to clusters. The circle with error bars corresponds to
  \bullg data reported from \citet{2013A&A...552A..80M} and
  \citet{Gastaldello}. The data used to construct the histograms
  integrates the objects at all redshifts. }
\label{fig:mass_displacement}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{figure_3.eps}
\end{center}
\caption{Integrated probability distribution for the relative velocity of the
sub-halo with respect to its host. The left panel shows the results
in physical units while the right panel show the same values
normalized by the circular velocity of the host halo. The line coding
follows the same structure as Figure \ref{fig:displacement}}
\label{fig:velocities}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{figure_4.eps}
\end{center}
\caption{x}
\label{fig:geometry}
\end{figure*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{figure_5.eps}
\end{center}
\caption{Integrated probability distribution for the estimated
  baryonic displacements in the group and cluster samples at all redshifts.}
\label{fig:baryonic_displacements}
\end{figure}

@@

The results for the integrated distributions for $>d_{2D}^{\rm bar}$
are shown in Figure \ref{fig:baryonic_displacements}. The dashed lines
represented the results for groups and the continous lines correspond
to clusters. As a test of our approach we compare the cluster results
against the analytic fit provided by \cite{ForeroRomero2010}. This fit
reproduces the statistics for the DM-baryon separation found for
clusters more massive than $>10^{14}$\hMsun in a simulation
that included a description for gas with $8$ times the volume of the
Bolshoi Simulation. This fit is valid for separations larger than
$70$\hkpc, beyond that separation we find that it provides a good
description within a factor of $\sim 2$ of

\subsection{Reproducibility of our results}
In order to facilitate the reproducibility and reuse of our results we
have made available all the data and the source code available in a public
repository. [...]

\section{Observational Implications}
\label{sec:observations}
